---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
#load the data
activityData <- read.csv(unz("activity.zip", "activity.csv"), stringsAsFactors=FALSE)
#transform the date column from string to date
activityData$date <- as.Date(activityData$date, '%Y-%m-%d')
```

## What is mean total number of steps taken per day?
* Make a histogram of the total number of steps taken each day
```{r}
activityDataByDate <- aggregate(activityData$steps, list(date = activityData$date), sum)
hist(activityDataByDate$x, xlab = "total number of steps", main = "Histogram of total number steps by date")
```

* Calculate and report the mean and median total number of steps taken per day
```{r}
mean(activityDataByDate$x, na.rm = TRUE)
median(activityDataByDate$x, na.rm = TRUE)
```

## What is the average daily activity pattern?
* Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
averageActivityData <- aggregate(activityData$steps, 
                                 list(interval=activityData$interval), mean, na.rm=TRUE)
plot(averageActivityData$interval, averageActivityData$x, type = 'l', ylab="average number of steps")
```

* Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
averageActivityData$interval[which.max(averageActivityData$x)]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
