---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r}
#load the data
activityData <- read.csv(unz("activity.zip", "activity.csv"), stringsAsFactors=FALSE)
#transform the date column from string to date
activityData$date <- as.Date(activityData$date, '%Y-%m-%d')
```

## What is mean total number of steps taken per day?
1. Make a histogram of the total number of steps taken each day
```{r}
activityDataByDate <- aggregate(activityData$steps, list(date = activityData$date), sum)
hist(activityDataByDate$x, xlab = "total number of steps", main = "Histogram of total number steps by date")
```

2. Calculate and report the mean and median total number of steps taken per day
```{r}
mean(activityDataByDate$x, na.rm = TRUE)
median(activityDataByDate$x, na.rm = TRUE)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
